Technical Report

### 2018-06-18 fully-abstract-comp/technical-report.tex
Changed reasonability to always hold for n=0.

\[
  \lrrg{\trust}(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : (\RegName \setminus (\{\pcreg \} \cup R))\fun \World \ldotp \\
      \quad W = \bigoplus_{r \in (\RegName\setminus (\{\pcreg,\rdata \} \cup R))} S(r) \wedge \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrvg{\trust}(S(r))
    \end{array}
            \right\}
\]
We write $\lrr(W)$ to mean $\lrr(\emptyset)(W)$. That is, if we do not need to exclude extra registers, then we simply omit that argument.
% DOMI 18-1-2018: the below remark is obsolete, so I commented it out.
% Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
%\dominique{18-1-2018: it might be convenient to exclude $\rdata$ from the $\lrr$ relation by default too. Check if we ever use it with other instantiations of R.}
% Lau 19-01-2018: Added rdata as default.
\lau{RESOLVED check what conditions need to have a ``square'' i.e. need approximation}
\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      (\isLinear{\src{\vsc_S}} \text{ iff } \isLinear{\vsc_T}) \wedge\\
      \exists r \in \dom(\pwheap), \sigrets,\sigcloss,\mscode \ldotp \pwheap(r) = (\pure,\_,H_\sigma) \tand \\
      \quad H_\sigma = H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc \tand \\
      \quad \npair[n']{\stpair[.]{\vsc_S}{\vsc_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W) \text{ for all $n' < n$}\wedge\\
      \quad (\isLinear{\src{\vsc_S}} \Rightarrow \\
      \qquad\forall W' \future W, W_o, n' < n, \npair[n']{\stpair[.]{\vsc_S'}{\vsc'_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
      \qquad \quad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o)) \wedge \\
      \quad (\nonLinear{\src{\vsc_S}} \Rightarrow \\
      \qquad \forall W' \future \purePart{W}, W_o, n' < n, \npair[n']{\stpair[.]{\vsc_S'}{\vsc'_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
      \qquad \quad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o))

@@

\dominique{The below is an experimental reformulation of the reasonability requirement for the FTLR and full abstraction formulation.  All remarks welcome..
  The main change is that it now says that after a call, the post-return code is also expected to behave reasonably under reasonable assumptions. 
}
\dominique{TODO: better name than ``reasonable'' for all of this.}
Take a block of code memory $\mscode$, a set of trusted addresses $\ta$ and sets of return pointer and closure seals $\sigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable up to $n$ steps in memory $\ms$ if the following implications hold.
\begin{itemize}
\item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\sigrets \cup \sigcloss)$
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \neq 0$ and $\sigrets \neq \emptyset$, then $[\baddr,\eaddr] \# \dom(\mscode)$
\item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\sigrets\cup \sigcloss)$ then $\vsc$ is reasonable.
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \in \readAllowed{}$ and $n > 0$, then $\ms(\aaddr)$ is reasonable up to $n - 1$ steps for all $\aaddr \in ([\baddr,\eaddr] \setminus \ta)$
\end{itemize}

We say that an execution configuration $\Phi$ is reasonable up to $n$ steps if:
  \begin{itemize}
  \item \emph{Guarantee stack base address before call} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\Phi'$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$ for some $\src{r_1}$ and $\src{r_2}$
    \item $i \le n$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi'}(\src{r_\stk}) = \src{\stkptr{\_,\stkb,\eaddr_\stk,\aaddr_\stk}}$
    \item $r_1 \neq \rtmp{1}$
    \item $\Phi'(\pcreg) + \calllen$ and $\Phi'(\rstk)$ behaves reasonably up to $n-i$ steps
    \end{itemize}
  \item \emph{Use return seals only for calls} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \item $i \le n$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi'}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$ and $\sigma \in \sigrets$ 
    \item $\sigma \in \sigcloss$.
    \end{itemize}
  \item \emph{Don't store private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then 
    \item $i \le n$
    \end{itemize}
    Then $\Phi.\reg(r_2)$ is reasonable in memory $\Phi'.\mem$ up to $n$ steps
  \item \emph{Don't leak private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi' \step \Phi''$
    \item $\src{\Phi'}$ is in $\ta$
    \item $\src{\Phi''}$ is not in $\ta$
    \item $i \le n$
    \end{itemize}
    Then $\Phi.\reg(r)$ is reasonable in memory $\Phi'.\mem$ up to $n$ steps for all $r$ (including $\pcreg$)
  \end{itemize}

>>>>

\[
  \lrrg{\trust}(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : (\RegName \setminus (\{\pcreg \} \cup R))\fun \World \ldotp \\
      \quad W = \bigoplus_{r \in (\RegName\setminus (\{\pcreg,\rdata \} \cup R))} S(r) \wedge \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrvg{\trust}(S(r))
    \end{array}
            \right\}
\]
We write $\lrr(W)$ to mean $\lrr(\emptyset)(W)$. That is, if we do not need to exclude extra registers, then we simply omit that argument.
% DOMI 18-1-2018: the below remark is obsolete, so I commented it out.
% Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
%\dominique{18-1-2018: it might be convenient to exclude $\rdata$ from the $\lrr$ relation by default too. Check if we ever use it with other instantiations of R.}
% Lau 19-01-2018: Added rdata as default.
\lau{RESOLVED check what conditions need to have a ``square'' i.e. need approximation}
\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      (\isLinear{\src{\vsc_S}} \text{ iff } \isLinear{\vsc_T}) \wedge\\
      \exists r \in \dom(\pwheap), \sigrets,\sigcloss,\mscode \ldotp \pwheap(r) = (\pure,\_,H_\sigma) \tand \\
      \quad H_\sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc \tand \\
      \quad \npair[n']{\stpair[.]{\vsc_S}{\vsc_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W) \text{ for all $n' < n$}\wedge\\
      \quad (\isLinear{\src{\vsc_S}} \Rightarrow \\
      \qquad\forall W' \future W, W_o, n' < n, \npair[n']{\stpair[.]{\vsc_S'}{\vsc'_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
      \qquad \quad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o)) \wedge \\
      \quad (\nonLinear{\src{\vsc_S}} \Rightarrow \\
      \qquad \forall W' \future \purePart{W}, W_o, n' < n, \npair[n']{\stpair[.]{\vsc_S'}{\vsc'_T}} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
      \qquad \quad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o))

@@

\dominique{The below is an experimental reformulation of the reasonability requirement for the FTLR and full abstraction formulation.  All remarks welcome..
  The main change is that it now says that after a call, the post-return code is also expected to behave reasonably under reasonable assumptions. 
}
\dominique{TODO: better name than ``reasonable'' for all of this.}
Take a block of code memory $\mscode$, a set of trusted addresses $\ta$ and sets of return pointer and closure seals $\sigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable up to $n$ steps in memory $\ms$ if $n=0$
or the following implications hold.
\begin{itemize}
\item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\sigrets \cup \sigcloss)$
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \neq 0$ and $\sigrets \neq \emptyset$, then $[\baddr,\eaddr] \# \dom(\mscode)$
\item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\sigrets\cup \sigcloss)$ then $\vsc$ is reasonable up to $n - 1$ steps.
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \in \readAllowed{}$ and $n > 0$, then $\ms(\aaddr)$ is reasonable up to $n - 1$ steps for all $\aaddr \in ([\baddr,\eaddr] \setminus \ta)$
\end{itemize}

We say that an execution configuration $\Phi$ is reasonable up to $n$ steps if:
  \begin{itemize}
  \item \emph{Guarantee stack base address before call} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\Phi'$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$ for some $\src{r_1}$ and $\src{r_2}$
    \item $0 < i \le n$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi'}(\src{r_\stk}) = \src{\stkptr{\_,\stkb,\eaddr_\stk,\aaddr_\stk}}$
    \item $r_1 \neq \rtmp{1}$
    \item $\Phi'(\pcreg) + \calllen$ and $\Phi'(\rstk)$ behaves reasonably up to $n-i$ steps
    \end{itemize}
  \item \emph{Use return seals only for calls} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \item $0 < i \le n$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi'}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$ and $\sigma \in \sigrets$ 
    \item $\sigma \in \sigcloss$.
    \end{itemize}
  \item \emph{Don't store private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then 
    \item $0 < i \le n$
    \end{itemize}
    Then $\Phi.\reg(r_2)$ is reasonable in memory $\Phi'.\mem$ up to $n$ steps
  \item \emph{Don't leak private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi' \step \Phi''$
    \item $\src{\Phi'}$ is in $\ta$
    \item $\src{\Phi''}$ is not in $\ta$
    \item $0 < i \le n$
    \end{itemize}
    Then $\Phi.\reg(r)$ is reasonable in memory $\Phi'.\mem$ up to $n$ steps for all $r$ (including $\pcreg$)
  \end{itemize}
